Pulling oral and IV data from CvTdb

### 2025-02-18 data-raw/RestrictiveClearance_comparison.Rmd
Added diff_log_cvt() call for oral and iv. Included Kd affinity plots in main Rmd.

```{r load_Kd}
load(paste0(Sys.getenv("OD_DIR"),
            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
)
```

>>>>

```{r load_Kd}
load(paste0(Sys.getenv("OD_DIR"),
            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
)
new.raw.httk.data %>%
  distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
           Fit) %>%
  na.omit() %>%
  mutate(Target_Chemical = (DTXSID %in% target_chems)) %>%
ggplot(
       aes(
         x = forcats::fct_reorder(DTXSID, Affinity.Kd.Low)
         )) +
  geom_linerange(aes(
    ymin  = Affinity.Kd.Low,
    ymax = Affinity.Kd.High,
    color = Target_Chemical
  ), alpha = 0.4) +
  geom_point(aes(
    y = Affinity.Kd.Med, color = Target_Chemical
  ), size = 0.75) +
  # facet_grid(cols = vars(Fit), space = "free_x", scales = "free_x") +
  scale_y_log10(labels = scales::label_log(digits = 1)) +
  scale_color_manual(values = c("black", "green4")) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5, face = "bold"),
        legend.position = "bottom") +
  labs(title = "Kd estimates across chemicals", x = NULL)

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Kd_estimates_initialsummary.png"),
       bg = "white",
       height = 4, width = 9
)
```

### 2025-02-18 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Added diff_log_cvt() call for oral and iv. Included Kd affinity plots in main Rmd.

    if (!identical(common_row_cvt[diff_col_common],
                   common_row_new[diff_col_common])) {
      msg_to_write <- c(msg_to_write,
                        "Data for same observation key_ids have changed.")
    }
    msg_to_write <- c(msg_to_write,
                      "================================\n")
  }
  return(cat(msg_to_write, sep = "\n"))
}
```

>>>>

    if (!identical(common_row_cvt[diff_col_common],
                   common_row_new[diff_col_common])) {
      msg_to_write <- c(msg_to_write,
                        "Data for same observation key_ids have changed.")
    }
    msg_to_write <- c(msg_to_write,
                      "================================\n")
  }
  return(cat(msg_to_write, sep = "\n"))
}
diff_log_cvt(cvt_df)
```
